Embracing the Laws of Physics: \\ Reversible Models of Computation

### 2017-12-21 survey/survey.tex
start on Data II writeup

\newcommand{\fin}[1]{\ensuremath{\left[#1\right]}}
\newcommand{\Nat}{\ensuremath{\mathbb{N}}}

@@

However, as permutations are untyped and act on the canonicalized version
of $n$-element sets (i.e. those sets where all the structure has been
forgotten), these are a rather pale shadow of the rich tapestry of
information-perserving transformation of structured data.

@@

>>>>

\newcommand{\fin}[1]{\ensuremath{\left[#1\right]}}
\newcommand{\Nat}{\ensuremath{\mathbb{N}}}
\newcommand{\true}{\mathit{true}}
\newcommand{\false}{\mathit{false}}

@@

However as permutations are untyped, and act on the canonicalized version
of $n$-element sets (i.e. those sets where all the structure has been
forgotten), these are a rather pale shadow of the rich tapestry of
information-perserving transformation of structured data.

@@

The elementary building blocks of type theory are the empty type
($\bot$), the unit type ($\top$), and the sum ($\uplus$) and product
($\times$) types.  These have a nice correspondance (Curry-Howard)
to logic:

\begin{center}
\begin{tabular}{c|c}
Logic & Types \\ \hline
$\true$ & $\top$ \\
$\false$ & $\bot$ \\
$\land$ & $\times$ \\
$\lor$ & $\uplus$ \\
\end{tabular}
\end{center}

This correspondance is rather fruitful. As logical expressions form
a semiring, we would expect that types too form a semiring. And indeed
they do -- at least up to \emph{type equivalence}.  The natural
numbers $\Nat$ are another semiring; it will turn out that, even though
the Curry-Howard correspondance has been extremely fruitful for
programming language research, it is the semiring $\Nat$ which
will be a better model for finite structured types.
